Classifier Construction

### 2019-05-02 Code/dallin_annotations/07_build_classifier.Rmd
I used error = TRUE to reveal code that had been commented-out (i.e. the confusion matrix).

# bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label), max.depth = 4,
#                eta = 0.2, nthread = 2, nrounds = 100, objective = logregobj, eval_metric = evalerror)
```

@@

### Get Predictions from the Model
Here, we let the model make predictions on our test dataset. We then compare the predictions to our actual labels to help us understand accuracy. 
```{r}
# test_data$prediction <- predict(bst, dtest1)
# 
# predict(bst, dtest1) %>% map_chr(function(x) ifelse(x > 0, "complaint", "non-complaint"))
#   
# 
# test_data <- test_data %>% 
#   mutate(predict_label = case_when(prediction > 0 ~ "Complaint",
#                                    TRUE ~ "Non-complaint"),
#          complaint_label = case_when(complaint_label == 1 ~ "Complaint",
#                                    TRUE ~ "Non-complaint")) %>% 
#   mutate(accuracy = predict_label == complaint_label)
```

### Look at the Confusion Matrix
This Confusion matrix helps us see how many false postives and false negatives we had. For example, there were 85 instances where a tweet was predicted as a complaint, but it was not (false positive), and 38 instances where a complaint was not predicted to be a complaint, when it actually was (false negative). Overall, the model had an 87.59% accuracy, which seems pretty good to me.  
```{r}
# confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))

>>>>

bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label), max.depth = 4,
               eta = 0.2, nthread = 2, nrounds = 100, objective = logregobj, eval_metric = evalerror)
```

@@

### Get Predictions from the Model
Here, we let the model make predictions on our test dataset. We then compare the predictions to our actual labels to help us understand accuracy. 
```{r}
test_data$prediction <- predict(bst, dtest1)

predict(bst, dtest1) %>% map_chr(function(x) ifelse(x > 0, "complaint", "non-complaint"))

test_data <- test_data %>%
  mutate(predict_label = case_when(prediction > 0 ~ "Complaint",
                                   TRUE ~ "Non-complaint"),
         complaint_label = case_when(complaint_label == 1 ~ "Complaint",
                                   TRUE ~ "Non-complaint")) %>%
  mutate(accuracy = predict_label == complaint_label)
```

### Look at the Confusion Matrix
This Confusion matrix helps us see how many false postives and false negatives we had. For example, there were 85 instances where a tweet was predicted as a complaint, but it was not (false positive), and 38 instances where a complaint was not predicted to be a complaint, when it actually was (false negative). Overall, the model had an 87.59% accuracy, which seems pretty good to me.  
```{r}
confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))
